BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-19 tex/2-algorithms.tex
Reformulated the beginning of related work

This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for authors, dates and comments. Our approach uses blog specific characteristics to build extraction rules which are applicable to all blog posts. Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.

@@

% per blog procedure, related work
To extract content from blog posts, we proceed by building extraction rules from the data given in the blog's web feed. The idea is to use a set of \emph{training data}, pairs of HTML pages and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.

% input from observations.
Observation \ref{havefeedAssum} allows the crawler to obtain input for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding web page as well as blog post article (either abstract or full text), its title, authors and publication date. We call these fields \emph{targets} as they constitute the data our crawler aims to extract. Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.

>>>>

This section explains in detail the algorithms we developed to extract blog post articles as well as its variations for authors, dates and comments. Our approach uses blog specific characteristics to build \emph{extraction rules} which are applicable to all blog posts. Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.

@@

% per blog procedure, related work
To extract content from blog posts, we proceed by building \emph{extraction rules} from the data given in the blog's web feed. The idea is to use a set of \emph{training data}, pairs of HTML pages and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.

% input from observations.
Observation \ref{havefeedAssum} allows the crawler to obtain input for the extraction rule generation algorithm: each web feed entry contains a link to the corresponding web page as well as blog post article (either abstract or full text), its title, authors and publication date. We call these fields \emph{targets} as they constitute the data our crawler aims to extract. Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.

### 2014-01-19 tex/5-related-work.tex
Reformulated the beginning of related work

\section{Related work}

\Anotecontent{wrapper}{In the literature, procedures to extract structured data from unstructured document are commonly referred as \emph{wrappers}. In this paper we decided to rather employ the less generic term of \emph{extraction rules} which is closer to our implementation.}

The BlogForever Crawler combines ideas from previous work on general web crawlers and extraction rule\Anote{wrapper} generation algorithms.

Research on large scale distributed crawler such as Mercator \cite{najork2001}, used by AltaVista, the spider discussed in \cite{shkapenyuk2002} or UbiCrawler \cite{boldi2003} are enlightening regarding the difficulties arising when scale out a crawler. One of the core issues seems to be in sharing the list URLs which have already been visited and need to be visited. While \cite{najork2001} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing. Both of these approaches require complex mechanisms to achieve fault tolerance. The BlogForever crawler circumvent this problem by delegating all state the back-end system. This shared nothing architecture between crawler instance is made possible by the fact that our unit of computations, crawling a entire blog, is much large than fetching a single URL and does not generate further crawling tasks. In addition, because we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side. This removes one layer of complexity when compared to general crawler which need use a distributed file system or implement an aggregation mechanism in order to further use the collected data.

\cite{shkapenyuk2002} used NFS, \cite{berger2011} uses HDFS

- Wrapper generation\\
these works do not clearly address how to extract other info link author and publication date, and do not include complexity analysis which is something that cannot be ignored when aiming for a universal large scale solution.

% Web archiving is a challenging and very interesting problem and has been the subject of many studies as well as the goal of several projects.
% \comment{Mention Internet Archive here and maybe another generic web archiving project}

% A fraction of web archiving studies and projects focus on the specific problem of blog harvesting and archiving.
% They focus on the unique nature of blogs as dynamic web resources with a usually common set of attributes.
% Each entry in a blog, commonly called a post, has a title, an author, a publication date, some content and possibly some descriptive tags.
% (In this section we review some studies and projects that introduce and describe such techniques.)

% Blogs are strongly associated with web feeds, using technologies such as RSS and Atom (expand and reference - needed?).
% Web feeds are structured documents (often XML-based) that advertize and provide access to a website's content.
% Given their format, web feeds constitute an excellent source for blog archiving.
% They do, however, present some problems: (a) web feeds contain only the latest posts of a blog (usually 20) and (b) web feeds may only provide a summary or a fraction of the entire content of each blog post.
% More advanced methods and techniques have to be employed in order to achieve quality blog archiving.

% Here mention projects that use web feeds for discovery and compare them to ours.
% \begin{itemize}
%   \item ( Zero-cost Labelling with Web Feeds for Weblog Data Extraction - http://www2013.org/companion/p73.pdf).
%   \item ( Self-supervised Automated Wrapper Generation for Weblog Data Extraction - https://github.com/OlivierBlanvillain/blogforever-crawler-publication/raw/master/papers/bncod\_published.pdf).
%   \item ( Archiving Data Objects using Web Feeds - http://hal.archives-ouvertes.fr/docs/00/53/79/62/PDF/iwawienna.pdf).
% \end{itemize}
% Some of these should also be in the comparison for extraction methods.

% Here mention projects that use other techniques for discovery and compare them to ours.
% \begin{itemize}
%   \item ???
% \end{itemize}

% Here mention projects that use various techniques for extraction and compare them to ours.
% \begin{itemize}
%   \item ( Web Object Identification for Web Automation and Meta-Search - http://www.dbai.tuwien.ac.at/proj/tamcrow/download/Kordomatis2013WIMS.pdf).
%   \item ( OXPath: A Language for Scalable, Memory-efficient Data Extraction from Web Applications - http://www.vldb.org/pvldb/vol4/p1016-furche.pdf).
%   \item ( Intelligent and Adaptive Crawling of Web Applications for Web Archiving - http://pierre.senellart.com/publications/faheem2013intelligent.pdf).
%   \item ( Web Data Extraction, Applications and Techniques: A Survey - http://www.emilio.ferrara.name/wp-content/uploads/2011/07/survey-csur.pdf).
% \end{itemize}

% Here mention that there is no comparison for the JavaScript rendering as there are no similar projects.
% \begin{itemize}
%   \item ???
% \end{itemize}

>>>>

\section{Related work}
\label{relatedwork}

Our crawler combines ideas from previous work on general web crawlers and \emph{wrapper} generation algorithms. The word \emph{wrapper} is commonly used to designate procedures to extract structured data from unstructured document. We did not employ this word in the present paper in favour of the term of \emph{extraction rule}, which better reflects our implementation and is decoupled from the XPath engine that concretely preforms the extraction.

Web crawling has been a well-studied topic over the last decade. One direction which we believe to be of crucial importance is the one of large scale distributed crawlers. Mercator \cite{heydon99mercator}, UbiCrawler \cite{boldi2003} and the crawler discussed in \cite{shkapenyuk2002} are examples of successful distributed crawler contain useful information regarding the challenges encountered when working on a distributed architecture. One of the core issues when scaling out seems to be in sharing the list URLs that have already been visited and need to be visited next. While \cite{heydon99mercator} and \cite{shkapenyuk2002} rely on a central node to hold this information, \cite{boldi2003} uses a fully distributed architecture where URLs are divided among nodes using consistent hashing. Both of these approaches require the crawlers to implement complex mechanisms to achieve fault tolerance.
%
The BlogForever Crawler circumvent this problem by delegating all state the back-end system. This shared nothing architecture between crawler instance is made possible by the fact that our units of computation, crawling entire blogs, is much large than fetching single URLs and does not generate further crawling tasks.
%
In addition, because we process web pages on the fly and directly emit the extracted content to the back-end, there is no need for persistent storage on the crawler side. This removes one layer of complexity when compared to general crawler which need use a distributed file system (\cite{shkapenyuk2002} uses NFS, \cite{berger2011} uses HDFS) or implement an aggregation mechanism in order to further exploit the collected data. Our design is inspired by the ideas of distributed active object presented in \cite{activeobject1996}.

A common approach in web content extraction is to manually build wrappers for the targeted websites. This approach has been proposed in the crawler discussed in \cite{faheem2012intelligent} which automatically categorising web sites according to the technology they use and use this information to obtain an appropriate wrapper from a knowledge base. The limiting factor of this type of approach is the high human resources needed to write and maintain the wrappers, which is not compatible with the increasing size and diversity of web.

these works do not clearly address how to extract other info link author and publication date, and do not include complexity analysis which is something that cannot be ignored when aiming for a universal large scale solution.
